%-------------------------
% Resume in Latex
% Author : Konstantin Tenman
%------------------------

\documentclass[11pt,a4paper,oneside]{report}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.35in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemWithoutTitle}[2]{
    \item\small{
        \textbf{#1}{#2\vspace{-2pt}}
    }
}


\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/ktenman}{\Large Konstantin Tenman}} & \href{tel:+3725111618}{+372 511 1618} \\
  Software Architect & \href{mailto:konstantin@tenman.ee}{konstantin@tenman.ee} \\
  Tallinn, Estonia & \href{https://github.com/ktenman}{https://github.com/ktenman} \\
   & \href{https://www.linkedin.com/in/ktenman}{https://www.linkedin.com/in/ktenman} \\
  \end{tabular*}

  %--------PROFILE------------
  \section{Profile}
  {Software Architect with 9+ years specializing in microservices architecture, DevOps, and fintech solutions. Extensive experience designing and maintaining scalable Spring Boot applications serving millions across financial services including payments, KYC, and regulatory compliance. Strong background in container technologies (Docker, Kubernetes) and CI/CD practices (Jenkins, GitLab CI/CD, GitHub Actions). Demonstrated track record in RESTful API design, database optimization (PostgreSQL), and implementing monitoring solutions. Proven leadership in mentoring engineering teams and delivering complex projects in agile environments. Technical achievements include: 50\% cost reduction through infrastructure optimization, 92\% API performance improvement (60ms to 5ms), and successful migration of 120M+ payment records. Currently leading AI initiatives at Cybernetica while maintaining expertise in enterprise Java development and cloud-native architectures.}

  %--------PROGRAMMING SKILLS------------
  \section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Languages}: Java, Kotlin, TypeScript, Python
      \hfill
      \textbf{Frameworks}: Spring Boot, Spring Framework, Hibernate, Angular, VueJS}
    \item
      \textbf{APIs \& Integration}: REST, Kafka, RabbitMQ
      \hfill
      \textbf{Testing}: JUnit, Mockito, WireMock, Selenide, AssertJ
    \item
      \textbf{Databases}: PostgreSQL, Redis
      \hfill
      \textbf{Containers}: Docker, Kubernetes
    \item
      \textbf{CI/CD \& DevOps}: Jenkins, GitLab CI/CD, GitHub Actions, Gradle, Maven, SonarQube
      \hfill
      \textbf{Monitoring}: Grafana, CloudWatch
    \item
      \textbf{Cloud \& Infrastructure}: AWS (ECS, Lambda), Tomcat
      \hfill
      \textbf{Version Control}: Git, GitHub, GitLab
    \item
      \textbf{Domains}: Fintech, Payments, KYC/AML, Regulatory Compliance (PSD2)
      \hfill
      \textbf{Languages}: English, Estonian, Russian
  \resumeSubHeadingListEnd


  %-----------EXPERIENCE-----------------
  \section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Cybernetica}{Tartu, Estonia}
  {Software Architect}{Jul 2024 - Present}
      \resumeItemListStart
          \resumeItemWithoutTitle{}
          {Technical Coordinator for EUCINF (EU Cyber \& Information Warfare R\&D project), leading cross-functional research teams in developing AI-powered microservices for European defense ministries.}
          \resumeItemWithoutTitle{}
          {Architected GPU-accelerated image-to-text microservice using Spring Boot, Kotlin, and REST APIs, implementing Docker containerization and CI/CD pipelines with Jenkins.}
          \resumeItemWithoutTitle{}
          {Designed scalable microservices architecture for R\&D prototypes supporting strategic, operational, and tactical use cases, utilizing PostgreSQL, Redis caching, and monitoring with Grafana.}
          \resumeItemWithoutTitle{}
          {Led technical specifications and architectural proposals for Estonian public sector AI implementations, collaborating with international stakeholders across multiple EU countries.}
      \resumeItemListEnd

  \resumeSubheading
  {University of Tartu}{Tartu, Estonia}
  {Teaching Assistant (Part-time)}{Aug 2022 - Jun 2025}
      \resumeItemListStart
          \resumeItemWithoutTitle{}
          {Teaching courses on Object-Oriented Programming in Java, Web Application Development, and Enterprise System Integration, contributing to the academic growth of students.}
      \resumeItemListEnd

  \resumeSubheading
  {Bankera}{Tallinn, Estonia}
  {Senior Software Engineer}{Jun 2022 - Jul 2024}
      \resumeItemListStart
          \resumeItemWithoutTitle{}
          {Led development and maintenance of KYC (Know Your Customer) microservices using Spring Boot and Java 8-21, implementing REST APIs and ensuring compliance with EU financial regulations.}
          \resumeItemWithoutTitle{}
          {Built robust, scalable solutions using PostgreSQL databases, Docker containerization, and GitLab CI/CD pipelines, achieving 80\% test coverage with JUnit, Mockito, and WireMock.}
          \resumeItemWithoutTitle{}
          {Designed and implemented RESTful APIs for financial services regulatory compliance system serving multiple banking clients across Europe, utilizing monitoring and logging best practices.}
          \resumeItemWithoutTitle{}
          {Collaborated in agile environment with cross-functional teams, participating in code reviews, architectural decisions, and knowledge sharing sessions.}
      \resumeItemListEnd

  \resumeSubheading
  {Monese}{Tallinn, Estonia \& London, UK}
  {Software Engineer $\rightarrow$ Technical Lead Engineer}{Oct 2017 - Jun 2022}
    \resumeItemListStart
      \resumeItemWithoutTitle{}
      {Promoted twice over 4 years, progressing from Software Engineer to Technical Lead Engineer, demonstrating consistent delivery and technical excellence in a high-growth fintech environment.}
      \resumeItemWithoutTitle{}
      {Led refactoring of monolithic application into single-responsibility microservices using Spring Boot, Docker, and Kubernetes. Designed RESTful APIs for payment processing, implementing Jenkins CI/CD pipelines.}
      \resumeItemWithoutTitle{}
      {Architected strong customer authentication (SCA PSD2) solution with comprehensive testing (JUnit, Mockito), facilitated technical brainstorming sessions, and mentored team members on microservices best practices.}
      \resumeItemWithoutTitle{}
      {Achieved 50\% reduction in monthly operating costs through performance optimization, infrastructure improvements, and implementation of monitoring solutions using Grafana and CloudWatch.}
      \resumeItemWithoutTitle{}
      {Successfully migrated 120M payments to queue-based Java microservice with zero downtime, reducing average API response time from 60ms to 5ms (92\% improvement) through architectural redesign.}
      \resumeItemWithoutTitle{}
      {Designed and developed Recurring Payments microservice with 80\%+ test coverage, implementing PostgreSQL database optimization, Redis caching, and comprehensive integration testing.}
      \resumeItemWithoutTitle{}
      {Enhanced microservice scalability by implementing database read/write segregation, optimizing SQL queries, and utilizing connection pooling to improve throughput and reduce contention.}
      \resumeItemWithoutTitle{}
      {Scaled and mentored engineering team from 5 to 12 members, conducting technical interviews, leading onboarding programs, and fostering DevOps culture through knowledge sharing sessions.}
    \resumeItemListEnd

  \resumeSubheading
  {Codeborne}{Tallinn, Estonia}
  {Software Developer}{Apr 2017 - Oct 2017}
    \resumeItemListStart
      \resumeItemWithoutTitle{}
      {Developed responsive internet banking applications using Java, Spring Framework, and RESTful APIs for Bank "Saint-Petersburg" (1M+ customers) and Czech online bank Expobank.cz.}
      \resumeItemWithoutTitle{}
      {Enhanced team productivity and code quality by conducting code reviews, implementing test-driven development practices, and promoting CI/CD best practices.}
    \resumeItemListEnd

  \resumeSubheading
  {Knowit}{Tallinn, Estonia}
  {Software Developer}{Jun 2016 - Apr 2017}
    \resumeItemListStart
      \resumeItemWithoutTitle{}
      {Recognized as Employee of Q4 2016 for outstanding contributions and exceptional code quality.}
      \resumeItemWithoutTitle{}
      {Developed full-stack web application enabling users to create and search for services via Google Maps integration, processing hundreds of daily searches.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------------
  \section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Tartu University}{Estonia}
  {Master of Science in Engineering (Computer Science); cum laude, GPA: 4.79/5}{}
  \resumeItemListStart
    \resumeItemWithoutTitle{}
    {Master's Thesis: ``AI-Powered MMSE: Enhancing Cognitive Assessment''}
    \resumeItemWithoutTitle{}
    {Recipient of Achievement and Specialisation stipends.}
  \resumeItemListEnd

  \resumeSubheading
  {Tallinn University}{Estonia}
  {Bachelor of Science in Engineering (Computer Science); cum laude; GPA: 4.72/5}{}
  \resumeItemListStart
      \resumeItemWithoutTitle{}
      {Bachelor's Thesis: ``The Development of a Self-study Web Application Using Angular and Spring Boot''}
      \resumeItemWithoutTitle{}
      {Recipient of Achievement and Specialisation stipends.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------PERSONAL PROJECTS-----------------
  \section{Personal Projects}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Portfolio Management System}{\href{https://github.com/ktenman/portfolio}{github.com/ktenman/portfolio}}
  {Full-Stack Investment Platform with Real-time Analytics}{Jul 2024 - Present}
      \resumeItemListStart
          \resumeItemWithoutTitle{}
          {Developed production-ready investment portfolio tracker with XIRR calculations, multi-provider market data integration (Alpha Vantage, Binance, FT), and automated performance analytics.}
          \resumeItemWithoutTitle{}
          {Implemented OAuth 2.0 authentication, Redis caching, scheduled jobs for price updates, and Telegram bot integration using Spring Boot 3.5 and Vue.js 3.}
          \resumeItemWithoutTitle{}
          {Achieved 70\% database load reduction through multi-level caching strategy and built comprehensive test suite with 80\%+ coverage.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------HOBBIES-----------------
%\section{Hobbies}
% \resumeSubHeadingListStart
%  \resumeItemWithoutTitle{Swimming}{}
% \resumeSubItem{Reading}{}
%  \resumeSubItem{Devclub.eu / Devclub.ee}
%   {It is a meeting held once a month where three presenters talk about topics
%  related to Information Technology.}
%  \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
